Breakpoint Models Show No Evidence of Recreational Adaptation to Increasing Wildfire Smoke in the American West

### 2021-05-24 MarkdownDocuments/Manuscript_Real.Rmd
plots 'n writing

### Validation
Due to the considerable computational time (about 1 day) needed to run the program described above, we validated the results of both the autoregressive-only and breakpoint models using within-sample posterior predictive checks. All models were first inspected to ensure adequate mixing of Markov chains and $\hat{R}$ values below 1.05 for all parameter estimates.

@@

# Results
While some between-park variation exists, our overall study shows no evidence for recreational visitor response to wildfire smoke in national parks in the American West.

@@

# Discussion
We probably need national level policy to protect people [@rai_policy_2020]. There is huge variation in the way states react and plan for climate change [@hu_evaluating_2018].

>>>>

### Validation
Due to the considerable computational time (about 1 day) needed to run the program described above, we validated the results of both the autoregressive-only and breakpoint models using within-sample posterior predictive checks. All models were first inspected to ensure adequate mixing of Markov chains, $\hat{R}$ values below 1.05 for all parameter estimates, and the absence of divergent transitions after warm up.

We examined the within-sample predictive capacity of the autoregressive only model to be sure we adequately accounted for baseline changes in visitation before building on this model to test for the effects of smoke on visitation. This baseline model allowed us to account for approximately 40% of all variation in the data, with the bulk of the error occurring when actual visitation was very high or very low (Fig 3).

@@

# Results
While some between-park variation exists, our overall study shows no evidence for recreational visitor response to wildfire smoke in national parks in the American West. Figures 4 and 5 show the parameter estimates for the pre and post breakpoint smoke effects respectively. In all three breakpoint models, only two parks have 90% credible intervals that do not overlap zero for slope 1, both of which have opposite signs (Fig. 4). This trend is paralleled for slope 2 in the two lower breakpoint models and all 90% credibility intervals overlap 0 for slope 2 in the model with the most extreme breakpoint (Fig. 5).

Intuitively, the within-sample $R^2$ increases only slightly when accounting for smoke effects, from 0.40 to 0.41 compared to the autoregressive only model. This suggests that ambiant smoke in national parks in the American West is not driving any measurable changes in visitation even at sustained and dangerous levels. We then conclude that visitors are not altering recreation behavior in response to smoke and therefore no critical threshold for adaptation is detectable in these data.

@@

# Discussion
We demonstrate that given the data available to us, we detect no visitor adaptation to increasing wildfire smoke in national parks in the American West. This result is troubling on both immediatly and in the long-term. We discuss earlier the public health dangers of wildfire smoke, and in particular $\text{PM}_{2.5}$.

We probably need national level policy to protect people [@rai_policy_2020]. There is huge variation in the way states react and plan for climate change [@hu_evaluating_2018].
